---
title: "p8105_hw5_md3851"
author: "Misbath Daouda"
date: "11/3/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1 

There are two cases to address:

For numeric variables, you should fill in missing values with the mean of non-missing values
For character variables, you should fill in missing values with "virginica"
Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.


```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  view()
```

```{r}
cleaning = function(x) {
  
   replace_na(x, "virginica")
  }
  
  
output = map(.x = iris_with_missing, ~ cleaning(.x))
output = map_dfr(.x = iris_with_missing, ~ cleaning(.x), .id = "input")
output %>%
  view()
```

